A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-02 ECCV/paper.tex
Changed figures, added discussion, incorporated Michael's changes.

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{multirow}
\usepackage{tabularx}
\setlength{\extrarowheight}{2pt}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\captionsetup[table]{belowskip=12pt,aboveskip=4pt}
\setlength{\floatsep}{7pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{7pt plus 2pt minus 2pt}
\setlength{\intextsep}{7pt plus 2pt minus 2pt}

@@

\begin{abstract}
This paper describes the design and evaluation of a binary fiducial marker
design for use with low-cost quadcopters.  Fiducial markers are commonly placed
into environments to provide a reliable and unique scene marker conducive for
tracking and recognition.   For quadcopter applications, fiducials are
typically used for evaluating planning algorithms by allowing ground truth
positions in the scene to be detected from the quadcopter's camera. Quadcopters,
however, are subject to quick and unstable motions that causes notable motion
blur that severely affects the detection rate of existing fiducial markers. 
This motivated us to design a fiducial that is robust to motion blur. Our design
uses a series of concentric circles with the observation is that the direction
perpendicular to the motion blur direction will be unaffected by the blur and
therefore still be recognized as a binary code.  We detail the design and
detection algorithm for our fiducial and show that our marker can significantly
outperform existing fiducials on scenes captured with a quadcopter.
\keywords{Fiducials, Tracking, Detection using Blur}
\end{abstract}

\section{Introduction}
Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
in various tracking activities e.g. aerial surveillance, search and rescue
operations etc. Navigation of these vehicles is mainly based on the
onboard inertial sensors. But sensor based measurments are prone to errors. So,
visual cues captured through onboard camera can be used along with the sensor
based measurments.  But, natural features may not be available always and
quality cannot be guaranteed in every scene. So, results are not satisfactory in
uncontrolled environment and hence use of such features is limited specifically
when we need very high precision.

Artificial markers are used when we need high precision. A fiducial marker or
simply a fiducial is an synthetic object placed in the scene, which can provide
additional information about the environment. Artificial fiducials are widely
used in Augmented Reality(AR) \cite{Zhang:2002}\cite{Dorfmuller99}
applications, vision based navigation of robots\cite{Davison:2007} etc.

Low cost quadcopters such as AR Drone are very unstable which
causes non-uniform motion resulting lot of motion blur in captured images.
Also, as image transfer is done through wireless media using User Datagram
Protocol (UDP), there is possibility of missing intermediate frames . It
results in lower frame rate (around 15 frames per second (FPS)) instead of
normal rate of 30 FPS. This frequent dropping of frames may cause drastic
change in position of object in successive frames. Thus, performance of
traditional tracking methods is not satisfactory for tracking through
quadcopters. Our aim is to design a fiducial which we will be able to track
under significant amount of motion blur and is robust in terms of drastic
change in its position in successive frames.

We observed that blur in a single frame captured through quadcopter is linear.
There is no blur in the direction perpendicular to the direction of motion. We
tried to design a fiducial whose ``signature'' remains intact in any direction.

\begin{figure}
\includegraphics[width=\linewidth]{teaser.pdf}
\caption{Figure showing experimental setup and comparison of
output of ALVAR\cite{alvar} (for detecting ARTag) versus output of our
algorithm, in normal and blurred scene}
\end{figure}

\section{Related Work}
Our work is related to two areas: fiducial markers and
object tracking. We will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}
\end{figure}

The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
Augmented Reality system, widely used to find pose of the object on which it is
placed.  Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
bi-tonal system consisting of a square border and
an interior region filled with a 6x6 grid of black or white cells. It proved to
be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
as well as the number of different patterns which can be created.

Concentric rings are reportedly used first by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
have developed ``Circular Data Matrix Fiducial System'', for wide area tracking.

Zhang el. al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
quite comprehensive comparative study of various fiducial marker systems with
respect to processing time, recognition rate and accuracy with
respect to viewing angle and distance.

@@

Before we detail the design of our fiducial, we examine the performance of two
popular fidicuals, ARTags and PiTags, in the face of motion blur.

We conducted a small experiment to test ARTag's resilience towards blur.
We scaled down ARTag fiducial to size 150x150.  Then, we blurred ARTag
at various orientations using different scales. Finally, we tried to detect
ARTag in these blurred images using ALVAR library\cite{alvar}.

@@

Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. The outermost and
innermost rings represent the start and end of the code and is embedded in the
fiducial; these are not considered part of the code itself. The binary code is
represented by the presence (or absence) of rings between ``marker'' rings.

Depending on which ring is present or absent, the resulting binary code will
change. The number of different patterns depends on the number of bits in the
binary code. For example, if the binary code has three bits, there will be a
maximum of three rings between``marker'' rings and we end up with eight
different patterns. Fig. \ref{fig:fiducials} shows two bit binary coded
fiducials.

\section{Fiducial Detection Algorithm}

@@

From Fig. \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
fails when blur scale is more than 15. The reason behind this is, Pi-tag
detection is based on Ellipse detection which will fail in the presence of
significant amount of blur. So, ellipse detection may not be the efficient way
to detect circular patterns under blur.

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\end{figure}
Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amount of blur.   In particular, we assume that scene motion 
blur be modelled locally as a linear motion blur~\cite{}.  Under this assumption,
scene content perpendicular to the blur direction is unaffected by the blur.  Because
of our circular design, this means the perpendicular direction can be observed as a 
unblurred linear pattern.  Figure \ref{fig:blur_direction} shows an example with
various motion directions.

@@

@@

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$). We have used following parameters for
creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
part)}$.
Then L2 norm of outputs along all orientations is calculated and finally, L2
normed image is binarized.

\begin{figure}
\centering
  \includegraphics[width=\linewidth]{training_data.pdf}  
  \caption{Training data for the fiducial pattern with binary code ``01''}
\end{figure}

@@

\textbf{Classification}: Each synthetic fiducial pattern is blurred along 36
orientations (0, 10, 20, \ldots , 350) and intensity profile along first
principal component from every output is taken as training data for that
fiducial pattern. Test pattern is matched against training data using 
K-Nearest Neighbor Classifier (K=5) to output class label.

@@

\section{Experimental Validation}

Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Fig.
\ref{fig:output0} -- Fig. \ref{fig:output3}.

@@

Our system has also been tested on images containing multiple fiducial patterns
in the same frame. Our algorithm successfully detected all fiducial patterns as
well as correctly classified them as shown in Fig. \ref{fig:output_all}
\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_all_2.jpg}
  \caption{Sample output containing all two bit binary coded fiducial patterns}
  \label{fig:output_all}
\end{figure}

\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker(BLUT)\cite{Wu:2011}.
\subsubsection{Comparison with ARTag}
First, we have repeated blur simulation experiment on our fiducials too, i.e.,
we have downsized our fiducial to size 150x150 and blurred it along various
orientations with different blur scales. Then, we tried to detect the patterns
using algorithm presented in earlier section. The comparison of recongition
rate is shown in Fig. \label{fig:recognition_rate}.

@@

\subsubsection{Comparison with BLUT} 
We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
and compare it with out result on the same image sequence. From Fig. \ref{fig:BLUT_output},
it can be inferred that BLUT is able to track the fiducial when the position of
fiducial doesnot change too much in successive frames. Also, it can be seen
that, once BLUT looses the track of the fiducial, it is not able to recover from
that. But, our algorithm is able to track the fiducial irrespecive of the change
in the position of the fiducial in the image as shown in Fig.
\ref{fig:our_output}.

@@

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output15.jpg}
\end{subfigure}
\caption{Output of our algorithm on image sequence used in
Fig. \ref{fig:BLUT_output}}
\label{fig:our_output}
\end{figure}

\section{Discussion}
\begin{itemize}
\item Processing Time
\item False Positives and False Negatives
\item Pose Estimation
\end{itemize}
\section{Conclusion and Future Work}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage{comment}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{multirow}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\captionsetup[table]{belowskip=12pt,aboveskip=4pt}
\setlength{\floatsep}{7pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{7pt plus 2pt minus 2pt}
\setlength{\intextsep}{7pt plus 2pt minus 2pt}

@@

\begin{abstract}
This paper describes the design and evaluation of a binary fiducial marker
for use with low-cost quadcopters.  Fiducial markers are commonly placed
in environments to provide a reliable and unique marker conducive for
tracking and recognition.   For quadcopter applications, fiducials are
typically used for evaluating planning algorithms by allowing ground truth
positions in the scene to be detected from the quadcopter's camera. Quadcopters,
however, are subject to quick and unstable motions that can cause significant motion
blur that severely affects the detection rate of existing fiducial markers.
This motivated us to design a fiducial that is robust to motion blur. Our design
uses a series of concentric circles with the observation is that the direction
perpendicular to the motion blur direction will be unaffected by the blur and
therefore still be recognizable.  We detail the design and
detection algorithm for our fiducial and show that our marker can significantly
outperform existing fiducial markers in scenes captured with a quadcopter.
\keywords{Fiducials, Tracking, Detection using Blur}
\end{abstract}

\section{Introduction}

The recent availability of low-cost quadcopters has help to fuel significant efforts in
research focused on Unmanned Aerial Vehicles.  Navigation and planning of
these vehicles is typically performed using onboard inertial sensors and/or
vision based modules that uses visual cues in the real world\cite{Davison:2007}. 
However, to evaluate the effectiveness of navigation methods, artificial
fiducial markers are commonly introduces into the environment to provide
additional information that often serves for ground-truth
measurements(e.g.\cite{Bosnak:2012}\cite{Lim09})

In order to be effective, fiducial markers (or simply called, fiducials) need
to be easily detected in the scene.  There are various existing commonly
used fiducial markers 
\cite{NaimarkF02}\cite{ARToolkit02}\cite{Fiala05}\cite{Pitag13}\cite{runetag11}.
These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02}\cite{Fiala05})
or other geometric features arranged in unique spatial patterns
(\cite{NaimarkF02}\cite{Pitag13}\cite{runetag11}).
Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
seen from a quad-copter.  One p roblem, however, is that low-cost quadcopters
often exhibit very quick and erratic motion.  These fast physical movements
results in motion blur in the quadcopters onboard camera.  Such motion blur has an adverse effect the
reconition of fiducial  markers.  This can be seen in Figure \ref{fig:teaser}(b)
where the ARTag cannot be recongized. This is not too surprising as most
fidicuals are not explicitly designed to handle motion blur.  Compounding this
problem is the common problem of dropped video frames from the quadcopters
wireless communication module.   This means that no only is blurring
introduced, but there may be large discountinues in the patterns position due
to missing video frames that makes tracking challenging.

To address this problem, propose a fiducial design that is robust to motion
blur and drastic drastic change in its position in successive frames.  Our
design is based on concentric circles as shown in Figure \ref{fig:fiducials}. 
The design is based on the observation that motion blur from a quadcopter tends
to be linear in nature.  As such, when our code is blurred, there is no blur in
the direction perpendicular to the direction of motion.   This allows the
signature of the fiducial to remain intact in any direction.  In addition, by
using concentric rings, we can treat them as bits allowing us to encode us
different fiducial identifers.  As far as we are aware, this is the first work
to design a blur resistent marker.   Our experiments show that this design can
significantly outperform existing codes in the face of motion blur.

The remainder of this paper is organized as follows.   Section 2 gives an
overview of related work, focused on fiducials as well the related problem of
tracking.  Section X discusses the our design and detection algorithm, by first
examining the performance of existing codes under blur. Section 3 shows several
experiments using quadcopter imagery.  This is followed by a discussion and
summary in Section 4 and 5 respectively.

\begin{figure}
\includegraphics[width=\linewidth]{teaser.pdf}
\caption{Figure showing experimental setup and comparison of
output of ALVAR\cite{alvar} (for detecting ARTag) versus output of our
algorithm, in normal and blurred scene}
\label{fig:teaser}
\end{figure}

\section{Related Work}

[For related work, you need to give more context of how these are related to your work. 
This is more of a list of papers and what they do, there relationship is not clear.]

Our work is related to two areas: fiducial markers and
object tracking. We will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}
\end{figure}

The ARToolkit \cite{ARToolkit02}\cite{kato-artoolkit} is well known toolkit in
Augmented Reality system, widely used to find pose of the object on which it is
placed.  Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
bi-tonal system consisting of a square border and
an interior region filled with a 6x6 grid of black or white cells. It proved to
be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
as well as the number of different patterns which can be created.

Concentric rings are reportedly used first by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
have developed ``Circular Data Matrix Fiducial System'', for wide area tracking. ....

Zhang et al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
quite comprehensive comparative study of various fiducial marker systems with
respect to processing time, recognition rate and accuracy with
respect to viewing angle and distance.

@@

We begin by first motivating the need for a new blur resistent fiducial by examining
the performance of prior fiducials under motion blur.  After this, we detail
our design as well as the detection algorithm used to find our marker in an image.

\subsection{Examining Prior Fiducials Under Motion Blur}

Before we detail the design of our fiducial, we examine the performance of two
popular fiducials under motion blur that have different designs. Specifically,
we examine ARTags\cite{Fiala05} and PiTags\cite{Pitag13}.

We scaled down ARTag as well as PiTag fiducial to size 150x150.  Then, we
blurred both fiducials at various orientations using different scales.
Figure \ref{fig:artag_pitag} shows sample blurred AR Tag and Pi-Tag. Finally, we
tried to detect ARTag using ALVAR library\cite{alvar} and Pi-Tag using\cite{ros_pitag}.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{artag_pitag.pdf}
\caption{Blurred AR Tag and Pi--tag with various blur scales}
\label{fig:artag_pitag}
\end{figure}

\begin{table}
\centering
\caption{Recognition rate of AR Tag and Pi-tag fiducial marker at various blur
scales}
\begin{tabularx}{0.75\textwidth}{|Y|Y|Y|}
\cline{1-3}
\multirow{2}{*}{Blur Scale} & \multicolumn{2}{c|}{Recognition Rate}
\\\cline{2-3}
 & AR Tag &	Pi-Tag \\ \cline{1-3}
15 & 100 & 100 \\ \cline{1-3}
30 & 0 & 100 \\  \cline{1-3}
35 & 0 & 19 \\ \cline{1-3}
50 & 0 & 0 \\ \cline{1-3}
\end{tabularx}
\label{tab:artag_pitag}
\end{table}

From Table \ref{tab:artag_pitag}, it can be clearly seen that performance of
ARTag as well as Pi-Tag drastically degrade with increase in blur scale.

\begin{comment}

@@

@@

From Figure \ref{fig:pitag_blur}, it can be seen that, Pi-tag detection
fails when blur scale is more than 15. The reason behind this is, Pi-tag
detection is based on Ellipse detection which will fail in the presence of
significant amount of blur. So, ellipse detection may not be the efficient way
to detect circular patterns under blur.
\end{comment}
We have designed a fiducial that may be thought of as a binary code.  It
contains concentric white rings of equal widths on a black background with a
blurred border. The outermost and innermost rings represent the start and end
of the code and is embedded in the fiducial; these are not considered part of
the code itself. The binary code is represented by the presence (or absence) of
rings between ``marker'' rings.

Depending on which ring is present or absent, the resulting binary code will
change. The number of different patterns depends on the number of bits in the
binary code. For example, if the binary code has three bits, there will be a
maximum of three rings between``marker'' rings and we end up with eight
different patterns. Figure \ref{fig:fiducials} shows two bit binary coded
fiducials.

\subsection{Fiducial Detection Algorithm}

@@

Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amount of blur.   In particular, we assume that scene motion
blur be modelled locally as a linear motion blur \cite{Moshe:2003,Moshe:2004}. 
Under this assumption, scene content perpendicular to the blur direction is 
unaffected by the blur.  Because of our circular design, this means the
perpendicular direction can be observed as a unblurred linear pattern.  Figure
\ref{fig:blur_direction} shows an example with various motion directions.

@@

Figure \ref{fig:overall_flow} shows the process involved in fiducial detection
process.

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\label{fig:overall_flow}
\end{figure}

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$). We have used following parameters for
creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
part)}$.
Then L2 norm of outputs along all orientations is calculated and finally L2
normed image is binarized.

\begin{figure}
\centering
  \includegraphics[width=\linewidth]{training_data.pdf}
  \caption{Training data for the fiducial pattern with binary code ``01''}
  \label{fig:training_data}
\end{figure}

@@

\textbf{Classification}: Each synthetic fiducial pattern is blurred along 36
orientations (0, 10, 20, \ldots , 350) and intensity profile along first
principal component from every output is taken as training data for that
fiducial pattern. Process of creation of training data for fiducial with
code ``01'' is depicted in Figure \ref{fig:training_data}. Test pattern is matched
against training data using K-Nearest Neighbor Classifier (K=5) to output class label.

@@

\section{Experimental Validation}
We have implemented our algorithm in C++ using OpenCV library. Our code was run
on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.

Our system has been tested on the image sequences captured from AR Drone
quadcopter. Each image sequence contains frames containing different fiducial
pattern. Sample output for each fiducial pattern is shown in Figure
\ref{fig:output0} -- Figure \ref{fig:output3}. Our detection process takes
around 0.3 seconds and can handle three to four frames per second.

@@

Our system has also been tested on images containing multiple fiducial patterns
in the same frame. Our algorithm successfully detected all fiducial patterns as
well as correctly classified them as shown in Figure \ref{fig:output_all}.
\begin{figure}
\centering
  \includegraphics[width=.8\linewidth]{output_all_2.jpg}
  \caption{Sample output containing all two bit binary coded fiducial patterns}
  \label{fig:output_all}
\end{figure}

\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker(BLUT)\cite{Wu:2011}.
\subsubsection{Comparison with ARTag}
First, we have repeated blur simulation experiment on our fiducials too, i.e.,
we have downsized our fiducial to size 150x150 and blurred it along various
orientations with different blur scales. Then, we tried to detect the patterns
using algorithm presented in earlier section. The comparison of recongition
rate is shown in Figure \ref{fig:recognition_rate}.

@@

\subsubsection{Comparison with BLUT}
We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
and compare it with out result on the same image sequence. From Figure \ref{fig:BLUT_output},
it can be inferred that BLUT is able to track the fiducial when the position of
fiducial doesnot change too much in successive frames. Also, it can be seen
that, once BLUT looses the track of the fiducial, it is not able to recover from
that. But, our algorithm is able to track the fiducial irrespecive of the change
in the position of the fiducial in the image as shown in Figure
\ref{fig:our_output}.

@@

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{output15.jpg}
\end{subfigure}
\caption{Output of our algorithm on image sequence used in
Figure \ref{fig:BLUT_output}}
\label{fig:our_output}
\end{figure}

\section{Discussion}

\textbf{Processing Time} :-  Currently our processing time (0.3 seconds per
frame) makes it difficult to do the fiducial detection in real-time. When we have
done the code profiling, we found that Gabor filter takes most of the time (0.03
-- 0.04 seconds perorientation). As we are applying Gabor filter along eight
orientations, we should think of some optimized way to do filtering.
Alternatively, some replacement for Gabor filter needs to be find out.

\textbf{False Negatives} :- We found that sometime our detection algorithm is
failed do recognize our fiducial with binary code ``0'' when there is large
amount of blur. This is the reason behing low recognition rate of ``00''
coded fiducial compared to that of our other fiducial patterns. When we
investigated the problem, we found that, if there is too much blur, the
innermost ring is not detected along the direction perpandicular to blur
direction. This problem can be resolved by increasing radius of innermost ring.

\textbf{Pose Estimation} :- Currently, we are not finding the pose from the
fiducial marker. But, if we put multiple markers (atleast four) in the same
scene, we may be able to find the pose. The current resolution of onboard camera
will be main hurdle to clear before we can effectively use multiple markers in
each scene.

\textbf{Number of Fiducials} :- Currently, compared to AR Tag fiducial markers,
we are able to generate less number of fiducials. Many applications in
robotics (e.g. qudcopter navigation) may not require large number of fiducial
markers as AR Tag. Most of the time, it is sufficient to have 4-6
different fiducial patterns. Still, we may be able to generate more number of
fiducials by using color background insted of black. E.g., if we just use Red,
Green and Blue as background color, number of fiducials will be increased by
factor of three.

\section{Conclusion and Future Work}
